---
  title: "Functions"
  editor_options: 
  chunk_output_type: console
---

This step will allow the creation of custom functions which will be later of use for the construction of sunburst plot. We are creating these custom functions as a way to simplify our code as well as a way to make it more understandable. Those custom functions will also allow the user to have a code frame where only their data input will be changed. This will make the code more stable and reliable. 

The first custom function will render possible the gathering of column of interest from the mother file of choice. This function will allow the user to replace both of those by: attributing the column of interest to "To_Replace" and the mother dataframe of choice to "Data_Of_Choice". This function use the `gather()` function to collect a set of wanted column names and places them into a single “key” column. We use this function twice. A first time, to gather the column samples of choice into a single column called "Taxonomy_Value", and a second time to gather the number of reads per "Taxonomy_Value". We then use the `group_by()` to group our two columns by the "Taxonomy_Value" column. Finally, the `summarise()` on the grouped data previously created by the `group_by()` function. This function applied to the number of reads per species will create one row for each "Taxonomy_Value". If ordered into a new object, this function will create a new data frame containing only the number of reads per taxonomy_value (species).

```{r, attr.source='.numberLines'}
Function_Gather <-function(To_Replace, Data_Of_Choice) {
 To_Replace <- enquo(To_Replace)
   Data_Of_Choice %>% 
  gather(key = "Sample", value = "Read", !!To_Replace) %>%
    gather(key = "taxonomy", value = "Taxonomy_Value", order:species) %>%
      group_by(Taxonomy_Value) %>%
        summarise(Total = sum(Read))
}
```

The second custom function will arrange a data frame to be assigned to "Name_Arrange" in a custom order. The `arrange()` and `match()` functions are used in this custom function to reorder the rows by one or more variable from the wanted column "Column_Of_Interest" which will be attributed to the object "Name_Taxonomy_Replace". 

```{r, attr.source='.numberLines'}
Function_Arrange <- function(Name_Arrange, Column_Of_Interest ,Name_Taxonomy_Replace){
Name_Arrange %>% 
  arrange(match(Column_Of_Interest, c(Name_Taxonomy_Replace)))
} 
```

The third custom function has for aim to create a data frame which can be use to create a Sunburt plot. In order to do so, we use the `data.frame()` function to create a dataframe with the different parameters needed for the construction of Sunburst plot. 

The sunburst sectors are determined by the entries in "ids", "labels" and "parents".
  - ids: This will assign id labels to each datum. These ids will be used as an object constancy of the different data points during the sunburst animation. They should only be an array of strings. 
  - labels: This will enable us to set the labels for each of the different sectors.
  - parents: This will set the parent sectors for each of the different created sectors. The use of empty string items '' will be understood as a way to reference the root node in the hierarchy. In this case, as the "ids" are filled, the "parents" items are understood to also be "ids" themselves.
  - size: This will attribute the size of each of the different sectors. 

```{r, attr.source='.numberLines'}
Function_DataFrame_Sb <- function(Data_Arrange_Taxonomy, Label_Order, Parent_Order, Data_Arrange_Total){
data.frame(
    ids = c(Data_Arrange_Taxonomy) ,
  labels = c(Label_Order),
  parents = c(Parent_Order),
  size = Data_Arrange_Total,
   stringsAsFactors = FALSE) 
}
```

The fourth and final custom function will be used to create and allow the Sunburst plot to be interactive. 
In order to do so, we use the `plot_ly()` function. the hovertext is attributed the data we want to appear as we hover the different sectors of the sunburst plot. 

```{r, attr.source='.numberLines'}
#This function will allow for the creation of the Sunburst Plot
Function_Sb <- function(Sunburst_Dataset, Dataset_Arrange_Total){
plot_ly(Sunburst_Dataset, 
        ids = ~ids, 
        labels = ~labels, 
        parents = ~parents, 
        type = 'sunburst',
        hovertext = ~Dataset_Arrange_Total,
        marker = list(colors = manualcolorSb))
}
```
